A Typed Programmatic Interface to Contracts on the Blockchain

### 2021-08-25 papers/execution-model/APLAS 2021/paper.tex
Add files via upload

Arguably, smart contracts are more useful if they can be
integrated with traditional software systems and thus triggered from
outside the blockchain.  Oracles
\cite{oracle-patterns,call-action-oracle} provide an approach for
contracts to obtain outside information. A contract registers a
request and a callback with an oracle. The oracle invokes the callback
as soon as an answer is available. The issue of trustworthiness of the
oracle arises because it is an entity outside of the blockchain, which
injects information into an otherwise closed, trusted (or trustless)
environment.

However, oracles are expensive and there are other usecases for
connecting a contract with traditional software. One example is
automatizing procedures like managing an auction, automatic bidding in
an auction, optimizing fees, or initiating delivery of goods to a
customer. While some of these procedures are amenable to
implementation as contracts, we might want to save the fee of running
them on the blockchain. In particular, for actions that happen
strictly within a single domain of trust, it is not worth running them
on the blockchain. For example, automated bidding runs on behalf of
a single peer.

Building such automation requires a programmatic interface to implement the interactions. 
Current blockchains mostly provide RPC interfaces, 
such as the Ethereum JSON-RPC API and the Tezos RPC API, but they
require cumbersome manipulation of string data in JSON format and do
not provide static guarantees (except that the response to a
well-formed JSON input is also a well-formed JSON output). 
To improve on this situation
we present a typed API for invoking contracts from OCaml programs. 
Our typed API supports the implementation of application programs and oracles 
that safely interact with smart contracts on the blockchain. 
Moreover, our approach provides a type-safe facility to communicate
with contracts where data is automatically marshalled between OCaml
and the blockchain. This interface is a step towards a seamless
integration of contracts into traditional programs.

>>>>

Arguably, smart contracts are more useful if they can be
integrated with traditional software systems and thus triggered from
outside the blockchain.  Oracles
\cite{oracle-patterns,call-action-oracle} provide an approach for
contracts to obtain outside information. A contract registers a
request and a callback with an oracle. The oracle invokes the callback
as soon as an answer is available. %The issue of trustworthiness of the oracle arises because it is an entity outside of the blockchain, which njects information into an otherwise closed, trusted (or trustless) environment.
%However, oracles are expensive and

There are other usecases for connecting a contract with traditional software. One example is
automating procedures like managing an auction,  bidding in
an auction, optimizing fees, or initiating delivery of goods to a
customer. While some of these procedures are amenable to
implementation as contracts, we might want to save the fee of running
them on the blockchain. In particular, for actions that happen
strictly within a single domain of trust, it is not worth running them
on the blockchain. For example, automated bidding runs on behalf of
a single peer.

Building such automation requires a programmatic interface to implement the interactions. 
Current blockchains mostly provide RPC interfaces, 
such as the Ethereum JSON-RPC API \cite{ethereum-rpc} and the Tezos RPC API \cite{tezos-whitepaper}, but they
require cumbersome manipulation of string data in JSON format and do
not provide static guarantees (except that the response to a
well-formed JSON input is also a well-formed JSON output). 
To improve on this situation
we present a typed API for invoking contracts from OCaml programs. 
Our typed API supports the implementation of application programs and oracles 
that safely interact with smart contracts on the blockchain. 
Moreover, our approach provides a type-safe facility to communicate
with contracts where data is automatically marshalled between OCaml
and the blockchain. This interface is a step towards a seamless
integration of contracts into traditional programs.
